Modelling small-area disease incidence data in space and time

### 2009-04-06 docs/dionne/slides.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@179 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Gonorrhoea in North Carolina}
describe data
map raw rates
map covariates, \% black, unemp
\end{frame}

@@

\begin{columns}
\column{0.5\textwidth}
\begin{block}{Where}
Predicted risk E$(\lambda_i | data)$

\end{block}
\column{0.5\textwidth}
\begin{block}{Why}
Predicted risk minus known risk factors \\
$E(\lambda_i - X_i \beta | data)= E(U_i + V_i)$

@@

\begin{frame}
\frametitle{Parameter estimates}
<<parest,result=tex,figure=false>>=
load("data\\GONQResult.RData")
library(glmmBUGS)
  gonpar = restoreParams(GONQResult, GONQragged$ragged)
  save(gonpar, file="gonpar.RData")
@
load("gonpar.RData")

@@

\begin{frame}
\frametitle{Parameter Estimates}

@@

\begin{frame}
\frametitle{E($W_{ij}$), time 1}

\begin{frame}
\frametitle{E($W_{ij}$), time 2}

>>>>

\begin{frame}
\frametitle{ North Carolina}
describe data
map raw rates
map covariates, \% black, unemp
\end{frame}

@@

\begin{block}{Where:
Predicted risk E$(\lambda_i | data)$}

\includegraphics[width=0.8\textwidth]{rate.png}
\end{block}

\begin{block}{Why:
Predicted risk minus known risk factors}
$E(\lambda_i - X_i \beta | data)= E(U_i + V_i)$

\includegraphics[width=0.8\textwidth]{relativeRate.png}

@@

\begin{frame}
\vspace*{-15pt}
Parameter estimates\\
\vspace*{-5pt}
{\small
<<parest,results=tex,fig=false>>=
if(F) {
load("data\\GONQResult.RData")
library(glmmBUGS)
  gonpar = restoreParams(GONQResult, GONQragged$ragged)
  save(gonpar, file="gonpar.RData")
}
load("gonpar.RData")
library(glmmBUGS)
gonSummary = summaryChain(gonpar)
par = rbind(gonSummary[[1]], gonSummary[[2]])

toprint =par[c(1,3,4,16:32),c(1,2,5,9)]
rownames(toprint) = gsub("_", "-" , rownames(toprint))
colnames(toprint) = gsub("%", "pct",colnames(toprint))
latex(toprint, file='', dec=2, rowlabel='Parameter')
@
}
\end{frame}

@@

\begin{frame}
\frametitle{Parameter Estimates}
<<parestst,results=tex,fig=false>>=

toprint =par[2:12,c(1,2,5,9)]
rownames(toprint) = gsub("_", "-" , rownames(toprint))
colnames(toprint) = gsub("%", "pct",colnames(toprint))
latex(toprint, file='', dec=2, rowlabel='Parameter')
@

@@

\begin{frame}
\frametitle{E($W_{ij}$), time 1}
\includegraphics[width=1.2\textwidth]{R05Q2.png}
\end{frame}

\begin{frame}
\frametitle{E($W_{ij}$), time 2}
\includegraphics[width=1.2\textwidth]{R05Q3.png}
\end{frame}

\begin{frame}
\frametitle{E($W_{ij}$), time 3}
\includegraphics[width=1.2\textwidth]{R05Q4.png}
\end{frame}

\begin{frame}
\frametitle{E($W_{ij}$), time 4}
\includegraphics[width=1.2\textwidth]{R06Q1.png}
\end{frame}

\begin{frame}
\frametitle{E($W_{ij}$), time 5}
\includegraphics[width=1.2\textwidth]{R06Q2.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 6}
\includegraphics[width=1.2\textwidth]{R06Q3.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 7}
\includegraphics[width=1.2\textwidth]{R06Q4.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 8}
\includegraphics[width=1.2\textwidth]{R07Q1.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 9}
\includegraphics[width=1.2\textwidth]{R07Q2.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 10}
\includegraphics[width=1.2\textwidth]{R07Q3.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 11}
\includegraphics[width=1.2\textwidth]{R07Q4.png}
\end{frame}
\begin{frame}
\frametitle{E($W_{ij}$), time 12}
\includegraphics[width=1.2\textwidth]{R08Q1.png}
\end{frame}
